Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
more rewording for risk and benefit rankings

Participants rated the the most familiar technologies as the most beneficial (top 5: internet, laptops, email, smartphones, and location tracking).  Again, we believe this is the result of exposure people have to these technologies--most people are exposed to these devices and use location-based applications. The most risky technologies were ones perceived to be privacy-invasive (bottom 5: facial recognition, internet, discreet video camera, location tracking, and facial detection). People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower. It is fair to say that, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.

>>>>

Participants rated the the most familiar technologies as the most beneficial; 5 most beneficial technologies were internet, laptops, email, smartphones, and location tracking. Again, we believe this is the result of exposure people have to these technologies--most people are exposed to these devices and use location-based applications. The most risky technologies were ones perceived to be privacy-invasive; 5 most risky technologies were facial recognition, internet, discreet video camera, location tracking, and facial detection. People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower. It is fair to say that, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.
